### 2017-06-20 sec-related-work.tex
Minor: change one citation format in related work.

Our formulation differs from both in that we do not feed the labeled
sequence of the lower level into the input of the higher level. Instead,
our lower level is actually treated using a non-hidden Markov model, and
the higher level is modeling transitions between the $K$ different
non-hidden Markov models we consider. The problem to be solved is similar
in that we wish to predict a ``label'' for a sequence of actions a student
takes as well as understand the transition behavior between those labels.
However, one of the consequences of modeling the lower layer using a
non-hidden Markov model instead of an HMM directly is that the meaning of
the $K$ different latent states can be more clearly captured by using our
proposed behavior representation. If we were to use an HMM as our first
layer, the behavior patterns (like from
Figure~\ref{fig:motivating-example}) would instead have nodes that
represent another set of latent states instead of being concrete actions
themselves. Each of these latent states would then be associated with some
other output distribution over the possible concrete actions to be
considered. In order to understand a single behavior pattern uncovered, one
would first have to understand the different output distributions for the
latent states in that pattern in order to understand the meaning of that
latent state. This further complicates the understanding of higher level
patterns because understanding the higher layer patterns requires
understanding the lower layer patterns. By taking a more restrictive view
on the first layer, we are able to produce a representation that can be
more readily interpreted due to the states in our first layer
representation having an immediately clear meaning (the concrete action
they represent).

>>>>

Our formulation differs from both \citet{Zhang:2004:CVPR} and
\citet{Oliver:2004:CVIU} in that we do not feed the labeled sequence of the
lower level into the input of the higher level. Instead, our lower level is
actually treated using a non-hidden Markov model, and the higher level is
modeling transitions between the $K$ different non-hidden Markov models we
consider. The problem to be solved is similar in that we wish to predict a
``label'' for a sequence of actions a student takes as well as understand
the transition behavior between those labels.  However, one of the
consequences of modeling the lower layer using a non-hidden Markov model
instead of an HMM directly is that the meaning of the $K$ different latent
states can be more clearly captured by using our proposed behavior
representation. If we were to use an HMM as our first layer, the behavior
patterns (like from Figure~\ref{fig:motivating-example}) would instead have
nodes that represent another set of latent states instead of being concrete
actions themselves. Each of these latent states would then be associated
with some other output distribution over the possible concrete actions to
be considered. In order to understand a single behavior pattern uncovered,
one would first have to understand the different output distributions for
the latent states in that pattern in order to understand the meaning of
that latent state. This further complicates the understanding of higher
level patterns because understanding the higher layer patterns requires
understanding the lower layer patterns. By taking a more restrictive view
on the first layer, we are able to produce a representation that can be
more readily interpreted due to the states in our first layer
representation having an immediately clear meaning (the concrete action
they represent).
